Data Preparation

### 2021-07-14 x0_data-preparation.Rmd
just a small correction to read the next lines

```{r}
sbgr_tl %>%
  ggplot() +
  geom_point(aes(x = DATE, y = DEP_DOM / N_DEP)) +
  theme_minimal()
```
```{r}
dep_vs_domshare <- function(.df){
  p <- .df %>%
  ggplot() +
  geom_point(aes(x = N_DEP, y = DEP_REG / N_DEP, colour = as.factor(year(DATE)))) +
  labs(colour = NULL) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)
                     ,expand = c(0,0)) +
  theme_minimal() +
  theme(legend.position = c(0.8, 0.8))
return(p)
}

>>>>

```{r}
sbgr_tl <- sbgr %>% apt_timeline()

sbgr_tl %>%
  ggplot() +
  geom_point(aes(x = DATE, y = DEP_DOM / N_DEP)) +
  theme_minimal()
```
```{r}
dep_vs_domshare <- function(.df){
  p <- .df %>%
  ggplot() +
  geom_point(aes(x = N_DEP, y = DEP_REG / N_DEP, colour = as.factor(year(DATE)))) +
  labs(colour = NULL) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)
                     ,expand = c(0,0)) +
  theme_minimal() +
  theme(legend.position = c(0.8, 0.8))
return(p)
}
